Increasing the topological gap by an order of magnitude through the geometry for Majorana SNS junctions.

### 2019-02-05 paper/snakemajoranas.tex
move the topological phase diagram to later in the manuscript
improve the phase diagram text

\comment{We calculate the topological phase diagram using the gap size.}
We calculate the gap $E_\textrm{gap}$ by finding the absolute minimum of the spectrum $E_\textrm{gap}=\min{|E(k)|}$.
Noting the gap closings and the fact we know the topology for the non-zigzag system, we can infer the topology of the system with zigzag modulation. % Bas: I don't understand what is written here

@@

>>>>

@@

\comment{We calculate the topological phase diagram using the gap size.}
Due to the large size of the system, we are unable to use full spectrum methods (like the Pfaffian) to compute the topological invariant of our system.
Instead, we calculate the gap by finding the absolute minimum of the spectrum $E_\textrm{gap}=\min{|E(k)|}$.
By both observing the gap closings and knowing the topological phase for the non-zigzag system, we can infer the topology of the system with zigzag modulation.
In Fig.~\ref{fig:phasediagrams}, we plot the energy gap as a function of magnetic field, chemical potential, $E_\textrm{gap}(B_x, \mu)$; and the superconducting phase difference $E_\textrm{gap}(B_x, \phi)$ for both a straight system [(a) and (b)] and a zigzag system [(c) and (d)].
